Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-23 Scripts/Initial_Analysis.Rmd
Modified F5 to match F4
Created Supplmental zoom figures of Fig5

##### Fig. 4N Mapping the time of emergence Of Top stocks

@@

###### The bar option by UN sub region

@@

##### Fig. 4. Bubble plot

@@

## Regional differences

@@

## Habitat preference differences

@@

####  Prooportion Analysis

##### Fig. 5 and S5. (Proportion + Netowrk)

# Done with the help of https://www.data-to-viz.com/story/MapConnection.html

@@

# Plot
p <-
  ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
  geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
  geom_sf(data = subset(sf_ready_plot, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
  my_ggtheme_m(leg_pos = "bottom") +
    geom_path(data = subset(arrows_data, percentage >= 0),
              aes(X, Y,
                  group = group,
                  col = percentage
              ),
              size = 1,
              arrow = arrow(length = unit(0.01, "npc"),
                            ends = "first"),
              show.legend = NA) +
  my_ggtheme_m(leg_pos = "bottom") +
  scale_color_gradientn(name= "Changes in catch proportion \nand changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(sf_ready_plot$percentage,na.rm=T)),
                        breaks = seq(0,max(sf_ready_plot$percentage,na.rm=T),10),
                        labels = c(seq(0,max(sf_ready_plot$percentage-10,na.rm=T),10),">50")
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion \nand changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(sf_ready_plot$percentage,na.rm=T)),
                        breaks = seq(0,max(sf_ready_plot$percentage,na.rm=T),10),
                        labels = c(seq(0,max(sf_ready_plot$percentage-10,na.rm=T),10),">50")
  )

name <- paste0("./Figures/ssr_",time_toplot,".png")
# Save figure
ggsave(plot =  p,
       name,
       width = 10,
       height = 5,
       units = "in")

@@

  Lat_am_data <- sf_ready_plot %>% 
    filter(source %in% Lat_am_eez$sf_eez_name)

  Lat_am_paths <- sf_ready_plot %>% 
    filter(source %in% Lat_am_eez$sf_eez_name,
           objective %in% Lat_am_eez$sf_eez_name)

@@

  Lat_am_map <- ggplot() +
    geom_sf(data = Lat_am_eez, size = 0.1, fill = "white", col = "gray30") +
    geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
    geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica" & time_step == time_toplot),
            aes(fill = avrg_spp_per),
            size = 0.1,col = "white") +
    geom_sf(data = Lat_am_points, aes(), color = "grey90") +
  my_ggtheme_m(leg_pos = "bottom") +
    geom_path(data = subset(Lat_am_paths, percentage > 0),
              aes(X, Y,
                  group = interaction(line_id,subline_id),
                  col = per_plot
              ),
              size = 1,
              arrow = arrow(length = unit(0.05, "npc"),
                            ends = "first"),
              show.legend = NA) +
    coord_sf(xlim = c(-100, -55),ylim = c(9, 30)) + 
    labs(x = "", y = "") +
    scale_x_continuous(breaks = seq(-100,60,10)) +
    scale_y_continuous(breaks = seq(10,30,10)) +
    my_ggtheme_m(leg_pos = "bottom") +
    theme(legend.position = "",
          panel.background = element_rect(fill = "white", color = "white"),
          panel.grid.major =  element_line(color = "white")
    ) +
    scale_colour_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Lat_am_data$percentage)),
      breaks = seq(0,max(Lat_am_data$percentage),10),
      # option="magma",
      # direction = -1
    )+
    scale_fill_viridis(
      name="Average Gain of\nStock-Share Ratio (%)",
      limits = c(0,max(Lat_am_data$percentage)),
      breaks = seq(0,max(Lat_am_data$percentage),10),
      # option="magma",
      # direction = -1
    )

  ggsave(plot =  Lat_am_map,
       "test.png",
       width = 10,
       height = 5,
       units = "in")

@@

>>>>

##### Fig. 4 Mapping the time of emergence Of Top stocks

@@

@@

@@

#### Regional differences

@@

#### Habitat preference differences

@@

##  Prooportion Analysis

### Fig. 5 and S5 Proportion + Netowrk

Note that this map is based on the data viz site: https://www.data-to-viz.com/story/MapConnection.html

```{r fig5_paths, eval = T, echo = T}

@@

# Plot
p <-
  ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
  geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
  geom_sf(data = subset(sf_ready_plot, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
    geom_path(data = subset(arrows_data, percentage >= 0),
              aes(X, Y,
                  group = group,
                  col = percentage
              ),
              size = 1,
              arrow = arrow(length = unit(0.01, "npc"),
                            ends = "first"),
              show.legend = NA) +
  my_ggtheme_m(leg_pos = "bottom") +
  scale_color_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(sf_ready_plot$percentage,na.rm=T)),
                        breaks = seq(0,max(sf_ready_plot$percentage,na.rm=T),10),
                        labels = c(seq(0,max(sf_ready_plot$percentage-10,na.rm=T),10),">50")
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(sf_ready_plot$percentage,na.rm=T)),
                        breaks = seq(0,max(sf_ready_plot$percentage,na.rm=T),10),
                        labels = c(seq(0,max(sf_ready_plot$percentage-10,na.rm=T),10),">50")
  ) + guides(
      color=guide_colorbar(title.position="top")
  ) +
  theme(legend.key.width = unit(4,"line"))

# name <- paste0("./Figures/ssr_",time_toplot,".png")
# Save figure
# ggsave(plot =  p,
#        name,
#        width = 8,
#        height = 5,
#        units = "in")

### Figure S6. Regional plots

Note that the following chunk needs the previous one to be ran

@@

  # Lat_am_land <- World_map %>% 
    # filter(region_wb %in% c("Latin America & Caribbean") |
             # sau_fishing_entity %in% c("USA","Mexico")
    # )

  Lat_am_eez <- World_eez_sf %>% 
    select(sf_eez_name = eez_name,everything()) %>% 
    left_join(Matching_names) %>% 
    filter(
      un_sub_region == "Latin America and the Caribbean",
      !str_detect(sf_eez_name,"Pacific"),
      !sf_eez_name %in% c("USA (East Coast)","Suriname","Guyana","French Guiana","Bermuda (UK)","Brazil","El Salvador")
    )

  Lat_am_data <- sf_ready_plot %>% 
    filter(source %in% Lat_am_eez$sf_eez_name,
           objective %in% Lat_am_eez$sf_eez_name)

  Lat_am_paths <- arrows_data %>% 
    filter(source %in% Lat_am_eez$sf_eez_name,
           objective %in% Lat_am_eez$sf_eez_name)

@@

  Lat_am_n_taxa <- n_taxa_map %>% 
    filter(
      region_wb == "Latin America & Caribbean",
      # !str_detect(sf_eez_name,"Pacific"),
      # !sf_eez_name %in% c("USA (East Coast)","Suriname","Guyana","French Guiana","Bermuda (UK)","Brazil","El Salvador")
    )

  lat_am_map <- ggplot() +
  geom_sf(data = Lat_am_eez, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(Lat_am_n_taxa, sovereignt != "Antarctica"),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
  # geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
  geom_sf(data = subset(Lat_am_data, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = Lat_am_points, aes(), color = "grey90") +
    geom_path(data = subset(Lat_am_paths, percentage >= 0),
              aes(X, Y,
                  group = group,
                  col = percentage
              ),
              size = 1,
              arrow = arrow(length = unit(0.01, "npc"),
                            ends = "first"),
              show.legend = NA) +
  my_ggtheme_m(leg_pos = "bottom") +
    coord_sf(xlim = c(-9000000,-5000000),ylim = c(1000000, 4000000)) + 
    labs(x = "", y = "") +
    # scale_x_continuous(breaks = seq(-100,60,10)) +
    # scale_y_continuous(breaks = seq(10,30,10)) +
    my_ggtheme_m(leg_pos = "bottom") +
    theme(
          panel.background = element_rect(fill = "white", color = "white"),
          panel.grid.major =  element_line(color = "white")
    ) +
    scale_color_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(Lat_am_data$percentage)),
                        breaks = seq(0,max(Lat_am_data$percentage),10)
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(Lat_am_data$percentage)),
                       breaks = seq(0,max(Lat_am_data$percentage),10)
  ) + guides(
      color=guide_colorbar(title.position="top", 
                        title.hjust =0.5)
  ) +
  theme(legend.key.width = unit(4,"line"))

  ggsave(filename = "lat_am_mid.png",
         lat_am_map,
         width = 6,
         height = 6)

  EU_data <- sf_ready_plot %>% 
    filter(source %in% EU_eez$sf_eez_name)

EU_map <- ggplot() +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
            aes(fill = avrg_spp_per),
            size = 0.1,
            col = "white") +
  # geom_sf(data = grey_land, size = 0.1, fill = "grey50", col = "gray30") +
  geom_sf(data = subset(sf_ready_plot, percentage >= 0), aes(color = percentage), size = 0.1, fill = "white") +
  geom_sf(data = point_data, aes(), color = "grey90") +
    geom_path(data = subset(arrows_data, percentage >= 0),
              aes(X, Y,
                  group = group,
                  col = percentage
              ),
              size = 1,
              arrow = arrow(length = unit(0.03, "npc"),
                            ends = "first"),
              show.legend = NA) +
  # my_ggtheme_m(leg_pos = "bottom") +
    coord_sf(xlim = c(-1300000,2000000),ylim = c(5500000, 7500000))  +
  labs(x = "", y = "") +
  scale_x_continuous(breaks = seq(-100,60,10)) +
  scale_y_continuous(breaks = seq(10,30,10)) +
    my_ggtheme_m(leg_pos = "bottom") +
    theme(
          panel.background = element_rect(fill = "white", color = "white"),
          panel.grid.major =  element_line(color = "white")
    ) +
    scale_color_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(EU_data$percentage)),
                        breaks = seq(0,max(EU_data$percentage),10)
  ) +
  scale_fill_gradientn(name= "Changes in catch proportion and changing stocks (%)",
                        colours = pal,
                        limits = c(0,max(EU_data$percentage)),
                       breaks = seq(0,max(EU_data$percentage),10)
  ) + guides(
      color=guide_colorbar(title.position="top",
                        title.hjust =0.5)
  ) +
  theme(legend.key.width = unit(4,"line"))

    ggsave(filename = "EU_early.png",
         EU_map,
         width = 6,
         height = 6)

@@

# Old code

## Fig. 4. Bubble plot

## Fig. 4N Top fishers on bars

The bar option by UN sub region of Figure 4N of top fishers
